### 2021-11-04 proposal-documents/white-paper/white-paper-general-preproposal.tex

%fonts
\usepackage{times}
%arial - uncomment next two lines
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}

\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
%\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
\usepackage[inline]{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}
%\usepackage{hyperref}
\usepackage{sectsty}
\usepackage{textcomp}
\usepackage{lastpage}
\usepackage{xargs} %for \newcommandx
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
\usepackage[toc,page]{appendix}
\usepackage[figure,table]{totalcount}
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries

@@

\section*{Abstract}
%may not be needed

@@

\subparagraph*(Key features of the project.)

\paragraph*{Motivation.}
\subparagraph*(Context.)

@@

\paragraph*{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project.

\paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
\subparagraph*{Task I. Title.}

\subparagraph*{Task II. Title.}

\paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
\subparagraph*{Task III. Title.}

\subparagraph*{Task IV. Title.}

\paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
\subparagraph*{Task VII. Crosscutting issues.}

@@

%\begin{table}[h!]
%    \centering
%    \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
%    \begin{tabular}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
\begin{longtable}{|L{0.17\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
%       \captionsetup{margin=-0pt}
        \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
        \label{tab-timeline}\\
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
        \multicolumn{4}{|c|}{\textbf{Y1}}&
        \multicolumn{4}{|c|}{\textbf{Y2}}&
        \multicolumn{4}{|c|}{\textbf{Y3}}
        \\
        \cline{2-13}
        &
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}
        \\
        \hline
        I. 
        &\x\textbf{X}
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        II. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        III. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        IV. 
        &\x\textbf{X}
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        V. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        VI. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        VII. Crosscutting issues
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        &\x\textbf{X} 
        &\x\textbf{X} 
        \\
        \hline
%    \end{tabular}
%    \label{tab-timeframe}
%\end{table}
\end{longtable}

@@

\begin{longtable}{|l|l|l|} %comment out for page limits
    \caption*{\textbf{Milestones.}}
    \label{tab-milestones}\\
    \hline
        \multicolumn{1}{|c|}{\textbf{Milestone}}
        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
        \hline
        \begin{tabular}[c]{@{}l@{}}
            0. Project logistics
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            0.1. Kick-off report, roles, and responsibilities.\\
            0.2. Annual reports.\\
            0.3. Agency administrative requirements.\\
            0.4. Final project report.\\
            0.5. Journal paper submission.\\
            0.6. Conference presentations.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            0.1. Y1-Q2\\
            0.2. Annually\\
            0.3. Quarterly\\
            0.4. Y3-Q4\\
            0.5. Annually\\
            0.6. Annually
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
            1.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            1.1.

@@

\newpage
%remove page break if there are page limits
%\vspace{0.5\baselineskip}

\section*{References}
\bibliographystyle{nsf}
\setlength{\bibhang}{0pt}
\bibliography{references}

>>>>

%%%%% fonts
\usepackage{times}
%arial - uncomment next two lines
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}
%%%%%

%%%%% references
%\usepackage[round,semicolon]{natbib} %for (Borrelli 2021; Clooney 2019) - standard.bst 
\usepackage[numbers,sort&compress]{natbib} %for [1-3] - nsf.bst, neup.bst
%%%%%

%%%%% tables and figures
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage{tablefootnote}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{tabto} %general tabbed spacing

\usepackage[singlelinecheck=false,labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup[table]{skip=7pt,labelformat={default},labelsep=period} %sets a space after table caption
\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format

\usepackage{wrapfig} %wraps figures around text
\setlength{\intextsep}{0.20mm}
\setlength{\columnsep}{0.20mm}
%%%%%

\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
\usepackage[inline]{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{lscape}
\usepackage{array}
\usepackage{chngcntr}
%\usepackage{hyperref}
\usepackage{sectsty}
\usepackage{textcomp}
\usepackage{lastpage}
\usepackage{xargs} %for \newcommandx
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
\usepackage[toc,page]{appendix}
\usepackage[figure,table]{totalcount}
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries

@@

%may not be needed
\begin{center}\subsection*{Abstract}\end{center}

@@

\subparagraph*{Key features of the project.}

\paragraph*{Motivation.}
\subparagraph*{Context.}

@@

\paragraph*{Logical Path, Work Scope, Description of Tasks.}

\paragraph*{Workscope 1 - Title.} (\textit{Lead - ; Support - })
\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{Title.}
    \item\textit{Title.}
    \item\textit{Title.}
\end{enumerate}

\paragraph*{Workscope 2 - Title.} (\textit{Lead - ; Support - })
\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{Title.}
    \item\textit{Title.}
    \item\textit{Title.}
\end{enumerate}

\paragraph*{Workscope 3 - Future outlook.} (\textit{Full team})
\begin{enumerate}[resume*,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{Crosscutting issues.}
\end{enumerate}

@@

\begin{longtable}{|L{0.23\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
%       \captionsetup{margin=-0pt}
        \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
        \label{tab-timeline}\\
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
        \multicolumn{4}{|c|}{\textbf{Y1}}&
        \multicolumn{4}{|c|}{\textbf{Y2}}&
        \multicolumn{4}{|c|}{\textbf{Y3}}
        \\
        \cline{2-13}
        &
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}
        \\
        \hline
        I. 
        &\x\textbf{X}
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        II. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        III. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        IV. 
        &\x\textbf{X}
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        V. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        VI. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        VII. Crosscutting issues
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        &\x\textbf{X} 
        &\x\textbf{X} 
        \\
        \hline
\end{longtable}

@@

%not typically needed in a preproposal, but good to do 
\begin{longtable}{|l|l|l|} %comment out for page limits
    \caption*{\textbf{Milestones.}}
    \label{tab-milestones}\\
    \hline
        \multicolumn{1}{|c|}{\textbf{Milestone}}
        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
        \hline
        \begin{tabular}[c]{@{}l@{}}
            0. Project logistics
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            0.1. Kick-off report, roles, and responsibilities.\\
            0.2. Annual reports.\\
            0.3. Agency administrative requirements.\\
            0.4. Final project report.\\
            0.5. Journal paper submission.\\
            0.6. Conference presentations.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            0.1. Y1-Q2\\
            0.2. Annually\\
            0.3. Quarterly\\
            0.4. Y3-Q4\\
            0.5. Annually\\
            0.6. Annually
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
            1.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            1.1.

@@

%remove page break if there are page limits
%\vspace{0.5\baselineskip}

\paragraph*{References}
\bibliographystyle{nsf}
\setlength{\bibhang}{0pt}
\bibliography{references}
